---
title: "Plots for Leverage Scrubbing Paper"
author: "Damon Pham"
date: "01/01/2021"
output: html_document
---

# Setup

```{r}
source("0_SharedCode.R")
stopifnot(SharedCode_version == c(11,0))
rm(iters); rm(omit_subjects)

subjects_S1200 <- readRDS(
  file.path(dir_data_misc, "HCP_S1200_LargeBalancedSample.rds")
)

hcp_dg_S1200 <- read.csv(hcp_dg_fname)
hcp_dg_S1200 <- subset(hcp_dg_S1200, Subject %in% subjects_S1200)
hcp_dg_S1200$Gender <- factor(hcp_dg_S1200$Gender)
hcp_dg_S1200$Age <- factor(hcp_dg_S1200$Age)

library(ggplot2)
library(ggpubr)
library(ggcorrplot)
library(viridis)
library(rgl)
library(misc3d)
library(cowplot)
library(RNifti)
```

### Colors & zlims

```{r}
color_pals <- list(
  Beach = data.frame(
    c = rev(c(
      "#4b063d", "#8018ad", "#6985f2", "#c7f1f9", "#e0fdec", 
      "#fffff5", "#fefbcb", "#f7ea74", "#ee8718", "#cf2f07", "#700202"
    )),
    v = 1 - c(0, .15, .25, .4, .45, .5, .55, .6, .75, .85, 1)
  ),
  Beach2 = data.frame(
    c = rev(c(
      "#2c308c", "#4f52a3", "#6985f2", "#c7f1f9", "#e0fdec", 
      "#fffff5", "#fefbcb", "#f7ea74", "#ee8718", "#d03a34", "#a81e22"
    )),
    v = 1 - c(0, .1, .225, .35, .425, .5, .575, .65, .775, .9, 1)
  ),
  virInfDiv = data.frame(
    c = rev(c(
      rev(viridisLite::inferno(20)), 
      "#000000", "#004ec3", "#1e91a4", "#11e27b", "#d7ffc9"
    )), 
    v = rev(1-c(seq(0, 1, 1/(20))/2, .65, .75, 0.85, 1))
  ),
  quickDiv = data.frame(
    c = c(
      "#0000ff", "#99bbff", "#ccffff", "#f9fff9", 
      "#ffffcc", "#ffbb99", "#ff0000"
    ),
    v = c(0, .4, .49, .5, .51, .6, 1)
  )
)

qd2 <- qd3 <- seq(0, 1, .1)
qd2[seq(5,7)] <- c(.48, .5, .52)
qd3[seq(5,7)] <- c(.32, .5, .58)

qS <- rev(RColorBrewer::brewer.pal(name="Spectral", n=11))
qS[6] <- "#FFFFFF"

coloring <- list(
  sequential = function(limits=c(0,1), ...){ viridis::scale_fill_viridis(option="inferno", limits=limits, ...) },
  sequential2 = function(limits=c(0,1), ...){ viridis::scale_fill_viridis(option="viridis", limits=limits, ...) },
  sequential3 = function(limits=c(0,1), ...){
    scale_fill_gradientn(
      colors=ciftiTools::ROY_BIG_BL()$color[seq(10, 19)], 
      values=(ciftiTools::ROY_BIG_BL()$value[seq(10, 19)]-.5)*2,
      limits=limits, ...
    )
  },
  diverging = function(limits=c(-1,1), ...){ 
    scale_fill_gradientn(colors=ciftiTools::ROY_BIG_BL()$color, values=ciftiTools::ROY_BIG_BL()$value, limits=limits, ...) 
  },
  diverging2 = function(limits=c(-1,1), ...){
    scale_fill_gradientn(colors=rev(RColorBrewer::brewer.pal(name="PuOr", n=9)), values=seq(0, 1, .1), limits=limits, ...)},
  diverging3 = function(limits=c(-1,1), ...){
    scale_fill_gradientn(colors=color_pals$Beach$c, values=color_pals$Beach$v, limits=limits, ...)
  },
  diverging4 = function(limits=c(-1,1), ...){
    scale_fill_gradientn(colors=color_pals$virInfDiv$c, values=color_pals$virInfDiv$v, limits=limits, ...)
  },
  diverging5 = function(limits=c(-1,1), ...){
    scale_fill_gradientn(colors=rev(color_pals$quickDiv$c), values=color_pals$quickDiv$v, limits=limits, ...)
  },
  diverging6 = function(limits=c(-1,1), ...){
    scale_fill_gradientn(colors=rev(RColorBrewer::brewer.pal(name="RdBu", n=11)), values=qd3, limits=limits, ...)
  },
  diverging7 = function(limits=c(-1,1), ...){
    scale_fill_gradientn(colors=color_pals$Beach2$c, values=color_pals$Beach2$v, limits=limits, ...)
  }
)

color_Rpals <- list(
  Set1 = RColorBrewer::brewer.pal(9, "Set1"),
  Set2 = RColorBrewer::brewer.pal(8, "Set2"),
  Set3 = RColorBrewer::brewer.pal(12, "Set3"),
  Pastel2 = RColorBrewer::brewer.pal(8, "Pastel2"),
  Paired = RColorBrewer::brewer.pal(12, "Paired"),
  Dark2 = RColorBrewer::brewer.pal(8, "Dark2"),
  Accent = RColorBrewer::brewer.pal(8, "Accent")
)

lim_FC <- .8
lim_cFC <- .015
lim_ICC <- .8
lim_cICC <- .1
```

### Parcellation and parcel labels

```{r}
# Get the labels (see "0_Labels" script).
q <- readRDS(file.path(dir_Parc, "ParcLabels.rds"))
PLabs <- q$PLabs
SLabs <- q$SLabs
Labs <- q$Labs
rm(q)

# Get the cortex parcellation.
NetMat <- read_cifti(file.path(dir_Parc, "Schaefer2018_400Parcels_Kong2022_17Networks_order.dlabel.nii"))
NetMat <- select_xifti(NetMat, idx=c(1,1))
NetMat$meta$cifti$labels[[1]][seq(parc_res)+1,c("Red", "Green", "Blue")] <- c(t(col2rgb(Labs$network_color[seq(parc_res)], alpha=FALSE))/255)
NetMatLabs <- rownames(NetMat$meta$cifti$labels$parcels)

color_network <- Labs[!duplicated(Labs$network_color),c("network", "network_color")]
color_network <- setNames(color_network$network_color, color_network$network)

Net <- list(
  levels=c(
    "all", "Aud", "Cont", "Default", "DorsAttn", "Language", 
    "SalVenAttn", "SomMot", "Visual", "Subcort",
    "Cerebellum", "Basal Ganglia", "Hippocampus-Amygdala", 
    "Brainstem-Diencephalon", "Thalamus",
    "CC", "CS", "SS"
  ), labels =c(
    "All", "A", "FP", "DMN", "dAttn", "L",
    "vAttn", "SMOT", "V", "SC",
    "CBLM", "BG", "H&A", 
    "B&D", "TH",
    "C-C", "C-SC", "SC-SC"
  )
)
```

### Masks for FC type

```{r}
get_FC_mask <- function(what){
  FC_is_level <- function(FC_level, FC_labels, intra=FALSE){
    FUN <- if (intra) { `&` } else { `|` }
    outer(FC_labels, FC_labels, function(x,y){FUN(x==FC_level,y==FC_level)})[upper.tri(diag(parc_res2))]
  }
  
  FC_is_same <- function(what){
    outer(Labs[[what]], Labs[[what]], `==`)[upper.tri(diag(parc_res2))]
  }
  
  wlabels <- Labs[[what]]
  wlevels <- if (is.factor(wlabels)) { levels(wlabels) } else { unique(wlabels) }
  mask <- list(
    inter = do.call(cbind, lapply(wlevels, FC_is_level, wlabels, intra=FALSE)),
    intra = do.call(cbind, lapply(wlevels, FC_is_level, wlabels, intra=TRUE)),
    same = FC_is_same(what)
  )
  colnames(mask$inter) <- colnames(mask$intra) <- wlevels
  mask$inter <- cbind(mask$inter, 1)
  colnames(mask$inter)[ncol(mask$inter)] <- "all"
  mask[c("inter", "intra")] <- lapply(
    mask[c("inter", "intra")], 
    function(x){t(t(x)/colSums(x))}
  )
  mask
}

FC_mask <- c("network", "group", "group2", "bs")
FC_mask <- as.list(setNames(FC_mask, FC_mask))
FC_mask <- lapply(FC_mask, get_FC_mask)
rm(get_FC_mask)
```

### FC grid plot

```{r}
# Variables
mbar_cols <- ifelse(is.na(Labs$group_color), Labs$network_color, Labs$group_color)[order(Labs$idx2)]
cor_mat_ylabs <- ifelse(
  c(Labs$network_first[rev(order(Labs$idx2))][seq(3, parc_res2)], FALSE, FALSE),
  Labs$network3[rev(order(Labs$idx2))], ""
)
gg_pdv <- which(Labs$network_first[order(Labs$idx2)])
gg_pdv <- gg_pdv[gg_pdv != 1]
divwidth <- .3
gg_pdv <- data.frame(xmin=gg_pdv-.5-(divwidth/2), xmax=gg_pdv-.5+(divwidth/2))
rm(divwidth)
gg_pdv$Var1 <- Var2 <- 0
pdv <- c(.5, gg_pdv$xmin + .15, parc_res2+.5) + .5 # "parc_div"

# Converted a vectorized lower triangular correlation matrix back to its full form.
cor_mat <- function(x_diag, diag_val=NA, names=NULL, newOrder=NULL, lowerOnly=FALSE) {
  d <- 1/2 + sqrt(1/4 + 2*length(x_diag))
  mat <- diag(d) * diag_val
  mat[upper.tri(mat)] <- x_diag
  mat <- t(mat)
  mat[upper.tri(mat)] <- x_diag
  if (!is.null(names)) { 
    stopifnot(length(names)==d); rownames(mat) <- colnames(mat) <- names 
  }
  if (!is.null(newOrder)) { 
    stopifnot(all(sort(newOrder) == seq(d))); mat <- mat[newOrder,rev(newOrder)] 
  }
  if (lowerOnly) { mat[seq(d), rev(seq(d))][lower.tri(mat)] <- NA }
  mat
}

ggcorrplot2 <- function(values, colFUN, title, legTitle, divColor="black", lim=NULL, diagVal=1){
  # Get cor mat
  mat <- values
  mat <- cor_mat(mat, names=Labs$label, newOrder=order(Labs$idx2))
  
  # Take network-network means in upper tri
  mat2 <- mat
  for (jj in seq(nrow(gg_pdv)+1)) {
    for (kk in seq(nrow(gg_pdv)+1)) {
      mat2[seq(pdv[jj], pdv[jj+1]-1), parc_res2+1 - seq(pdv[kk], pdv[kk+1]-1)] <- mean(
        mat2[seq(pdv[jj], pdv[jj+1]-1), parc_res2+1 - seq(pdv[kk], pdv[kk+1]-1)], na.rm=TRUE
      )
    }
  }
  mat[is.na(mat)] <- diagVal
  mat[seq(nrow(mat)), rev(seq(ncol(mat)))][lower.tri(mat)] <- mat2[seq(nrow(mat)), rev(seq(ncol(mat)))][lower.tri(mat)]

  # Limits
  if (!is.null(lim)) { 
    if (length(lim)==1) { lim <- c(-lim, lim) }
    mat[] <- pmax(lim[1], pmin(lim[2], mat))
  } else {
    lim <- max(abs(mat[]))
    lim <- c(-lim, lim)
  }

  ggcorrplot(mat, outline.color = "#00000000", title=title, digits=12) + 
    scale_y_discrete(labels=cor_mat_ylabs) +
    coord_equal(xlim=c(-4-10, parc_res2+.65), ylim=c(.5, parc_res2+5+10), expand=FALSE) +
    colFUN(
      c(lim[1], lim[2]), guide=guide_colorbar(ticks.colour = divColor, ticks.linewidth = 1), 
      labels = function(x){gsub("0.", ".", x, fixed=TRUE)}, na.value="red"
    ) +
    labs(fill=legTitle) +
    theme(
      panel.grid.major = element_blank(),
      axis.text.y = element_text(margin=margin(r=10)),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      legend.position = "bottom"#, legend.text.align = 1
    ) +
    # annotate(
    #   "raster", x=seq(119), y=rev(seq(119)), fill=divColor
    # ) +
    # brain region label color bar
    annotate(
      "rect", xmin=-4-10, xmax=.5, ymin=parc_res2+.5-seq(nrow(mat)), ymax=parc_res2+.5-seq(nrow(mat))+1,
      fill=mbar_cols[seq(nrow(mat))]
    ) +
    annotate(
      "rect", ymin=parc_res2+.5, ymax=parc_res2+5+10, xmin=seq(nrow(mat))-.5, xmax=seq(nrow(mat))+.5,
      fill=mbar_cols[seq(nrow(mat))]
    ) +
    # dividers
    geom_rect(aes(xmin=xmin, xmax=xmax, ymin=0, ymax=parc_res2+5+10), data=gg_pdv, fill=divColor) +
    geom_rect(aes(ymin=parc_res2+1-xmin, ymax=parc_res2+1-xmax, xmin=-4-10, xmax=parc_res2+.5), data=gg_pdv, fill=divColor) + 
    # four edges
    annotate("rect", xmin=.35, xmax=.65, ymin=0, ymax=parc_res2+5+10, fill=divColor) +
    annotate("rect", xmin=parc_res2+.35, xmax=parc_res2+.65, ymin=0, ymax=parc_res2+5+10, fill=divColor) + 
    annotate("rect", ymin=.35, ymax=.65, xmin=-4-10, xmax=parc_res2+.85, fill=divColor) +
    annotate("rect", ymin=parc_res2+.35, ymax=parc_res2+.65, xmin=-4-10, xmax=parc_res2+.85, fill=divColor) +
    # separate brain region label color bar
    annotate("rect", ymin=0, ymax=parc_res2+.65, xmin=-.5-3, xmax=.35, fill="white") +
    annotate("rect", ymin=parc_res2+.65, ymax=parc_res2+1.5+3, xmin=-.5, xmax=parc_res2+.65, fill="white")
}
```

### Helper functions

```{r}
load_a_result <- function(names, what="reliability", nT=1185, S1200=FALSE){
  x <- lapply(
    file.path(
      dir_analysis, what, 
      paste0(names, "_", nT, ifelse(S1200, "_S1200.rds", ".rds"))
    ),
    function(y){if(file.exists(y)){return(readRDS(y))}else{return(NULL)}}
  )
  
  if (what=="reliability") {
    x <- list(
      MSB=lapply(x, `[[`, "MSB"),
      MSR=lapply(x, `[[`, "MSR"),
      ICC31=lapply(x, `[[`, "ICC31")
    )
  } else {
    x <- setNames(list(x), what)
  }
  x
}

# For appendix
get_ggs <- function(x, group=c("Proj", "FD")){
  group <- match.arg(group, c("Proj", "FD"))
  x2 <- expand.grid(
    network = rownames(x[[1]][[1]]),
    method = colnames(x[[1]][[1]]),
    what = names(x[[1]]),
    nT = names(x)
  )
  
  x2$value <- do.call(c, lapply(x, function(x){do.call(c, lapply(x, c))}))
  attr(x2$value, "dimnames") <- NULL
  stopifnot(
    x$T800$ICC31["DorsAttn",colnames(x$T400$ICC31)[5]] == subset(
      x2, network=="DorsAttn" & method==colnames(x$T400$ICC31)[5] & what=="ICC31" & nT=="T800"
    )$value
  )
  
  x2$method <- as.character(x2$method)
  x2$method[grepl("Base", x2$method)] <- "Base"
  x2$method[grepl("DVARSdual", x2$method)] <- "DVARSdual"
  if (group=="Proj") {
    x2$isProj <- grepl("Lev___", x2$method)
    x2$method <- gsub("Lev___", "", x2$method)
    x2$kurt <- grepl("kurt", x2$method)
    msplit <- strsplit(x2$method, "_")
    x2$method2 <- factor(
      vapply(msplit, function(x){x[1]}, ""),
      levels=c("Base", "DVARSdual", "ICA", "PCA", "fusedPCA")
    ) 
  } else if (group=="FD") {
    msplit <- strsplit(x2$method, "_")
    x2$dt <- grepl("dt", x2$method)
    x2$l4 <- grepl("l4", x2$method)
    x2$filter2 <- ifelse(grepl("nfb", x2$method), "Bw", ifelse(grepl("nfc", x2$method), "Cb", "No"))
    x2$filter <- factor(x2$filter2, levels=c("Bw", "Cb", "No"), labels=c("Butterworth", "Chebyshev", "NoFilter"))
    x2$subgroup <- factor(paste0(ifelse(x2$l4, "Lag-4", "Lag-1"), ", ", x2$filter))
  }
  x2$cut <- suppressWarnings(
    as.numeric(vapply(msplit, function(x){x[length(x)]}, ""))
  )
  x2$method <- factor(x2$method)
  
  x2
}
```

```{r}
plt_fmt <- function(fname){file.path(dir_plots, paste0(sprintf("%02d", plt_idx), "_", fname))}
```

### Begin making plots

```{r}
plt_idx <- NA
varKeep <- c("varKeep", ls())
```

# 0. Kurtosis (App Figs.)

```{r}
plt_idx <- 0
source("6_Plots_1_Kurtosis.R")
rm(list=setdiff(ls(), varKeep))
```

# 1. Parcellation 

```{r}
plt_idx <- 1
source("6_Plots_2_Parcellation.R")
rm(list=setdiff(ls(), varKeep))
```

# 2. Flowchart

```{r}
plt_idx <- 2
rm(list=setdiff(ls(), varKeep))
```

# 3. Scrubbing example 

```{r}
plt_idx <- 3
rm(list=setdiff(ls(), varKeep))
```

# 4. Denoising & FC strength 

```{r}
plt_idx <- 4
```

### FC strength grid plot

```{r}
toShow <- list(
  c("Baselines_HCP__ICA-FIX", "Baselines_HCP__ICA-FIX_1185", "HCP ICA-FIX"),
  c("Baselines_None", "None__DCT4", "DCT4"),
  c("Baselines_None", "None__DCT0", "MPP"),
  c("Baselines_CC2MP", "CC2MP__06P_DCT4", "CC2MP6"),
  c("Baselines_36P", "36P__whole_DCT4", "36P")
)

pdf(plt_fmt("FC_strength_grid.pdf"))
for (ii in seq(length(toShow))) {
  q <- load_a_result(toShow[[ii]][1], "meanFC")
  q <- q$meanFC[[1]][,toShow[[ii]][2]]
  
  q <- ggcorrplot2(
    q, coloring$diverging7, divColor="black",
    paste("Mean FC:", toShow[[ii]][3]), 
    "FC", lim=lim_FC
  )
  print(q)
  
} 

dev.off()
```

### FC strength change on the brain surface

```{r}
xii0 <- convert_xifti(move_from_mwall(select_xifti(NetMat, 1)))
xii1 <- read_xifti(ciftiTools.files()$cifti["dscalar_ones"], brainstructures="sub")
qB <- load_a_result("Baselines_None", "meanFC")$meanFC[[1]][,"None__DCT0"]
for (ii in seq(length(toShow))) {
  q <- load_a_result(toShow[[ii]][1], "meanFC")
  q <- q$meanFC[[1]][,toShow[[ii]][2]]
  q <- rowMeans(cor_mat(q - qB), na.rm=TRUE)
  q0 <- newdata_xifti(xii0, c(0, q)[1+as.matrix(move_from_mwall(NetMat, 2))[,1]])
  plot(
    q0, title=toShow[[ii]][3], zlim=c(-lim_FC, lim_FC),
    colors=data.frame(color=rev(color_pals$Beach2$c), 
                      value = rev(color_pals$Beach2$v)*.2 - .1),
                      # value=rev(color_pals$Beach2$v)*lim_FC - lim_FC/2),
    fname=plt_fmt(paste0("FC_strength_change_onSurf_", toShow[[ii]][3], ".png"))
  )
  q1 <- newdata_xifti(xii1, c(0, q)[400+as.numeric(xii1$meta$subcort$labels)-2])
  plot(
    q1, title=toShow[[ii]][3], zlim=c(-lim_FC, lim_FC),
    colors=data.frame(color=rev(color_pals$Beach2$c), 
                      value = rev(color_pals$Beach2$v)*.2 - .1),
                      # value=rev(color_pals$Beach2$v)*lim_FC - lim_FC/2),
    fname=plt_fmt(paste0("FC_strength_change_onSub_", toShow[[ii]][3], ".png"))
  )
}

rm(list=setdiff(ls(), varKeep))
```

### Change dot plot

```{r}
qB <- load_a_result("Baselines_None", "meanFC")$meanFC[[1]][,"None__DCT0"]
qA <- load_a_result("Baselines_CompCor", "meanFC")$meanFC[[1]][,"CompCor__PC02_withCblm_DCT4"] - qB

q_gg <- data.frame(
  b=qB,
  a=qA,
  show=!FC_mask$bs$inter[,"subcort"],
  inter=!FC_mask$bs$same
)
q_gg$inter <- factor(ifelse(q_gg$inter, "Inter-hemispheric", "Intra-hemispheric"))
q_gg <- subset(q_gg, show); q_gg$show <- NULL
q_gg_s <- q_gg[with(set.seed(0), sample(nrow(q_gg), 40000)),]

q_gg_q <- vector("list", length(levels(q_gg_s$inter)))
qcut <- .05
for (ii in seq(length(levels(q_gg_s$inter)))) {
  il <- levels(q_gg_s$inter)[ii]
  q <- quantile(subset(q_gg_s, inter==il)$b, c(qcut, 1-qcut))
  q_gg_q[[ii]] <- subset(q_gg_s, (inter==il) & (b > q[1] & b < q[2]))
  #q_gg_q[[ii]] <- q_gg_qcut#data.frame(b=q, q=c(qcut, 1-qcut), inter=il)
}
q_gg_q <- do.call(rbind, q_gg_q)

pdf(plt_fmt("FC_strength_change.pdf"), width=8, height=5)

ggplot(q_gg, aes(x=b, y=a, color=inter)) + 
    geom_point(aes(shape=inter), alpha=.02, size=2) + 
    scale_shape_manual(values=c(16,16), guide="none") +#4,16
    cowplot::theme_cowplot() + 
    scale_y_continuous(breaks=c(-.1, 0, .1, .2), labels=c("-0.1", "0", ".1", "0.2")) +
    coord_cartesian(xlim=c(0, .7), ylim=c(-0.12, .22), expand=TRUE) +
    #coord_equal() + 
    #geom_vline(aes(xintercept=x, color=bs), data=c_gg_q) +
    geom_hline(yintercept=0, color="black", linetype="dashed") +
    #geom_line(aes(x=x, y=y), data=data.frame(x=seq(0, 1), y=seq(0, 1)), color="black", linetype="dashed") +
    scale_color_manual(values=c("#1c4e80", "#ac3e31"), name="") +
    geom_smooth(data=q_gg_q, method="loess", size=1, se=FALSE) +
    theme(
      legend.position="bottom", 
      axis.title.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0))
    ) +
    guides(color=guide_legend(nrow=1)) +
    xlab("FC after MPP") + ylab("FC change due to CC2MP6 denoising") + 
    guides(color=guide_legend(override.aes=list(size=3, fill=NA), nrow=1))

dev.off()

rm(list=setdiff(ls(), varKeep))
```

# 5. Denoising & FC reliability

```{r}
plt_idx <- 5
```

### FC reliability grid plot

```{r}
toShow <- list(
  c("Baselines_HCP__ICA-FIX", "Baselines_HCP__ICA-FIX_1185", "HCP ICA-FIX"),
  c("Baselines_None", "None__DCT4", "DCT4"),
  c("Baselines_None", "None__DCT0", "MPP"),
  c("Baselines_CC2MP", "CC2MP__06P_DCT4", "CC2MP6"),
  c("Baselines_36P", "36P__whole_DCT4", "36P")
)

pdf(plt_fmt("FC_reliability_grid.pdf"))
for (ii in seq(length(toShow))) {
  q <- load_a_result(toShow[[ii]][1], "reliability")
  q <- q$ICC31[[1]][,toShow[[ii]][2]]
  
  q <- ggcorrplot2(
    q, coloring$sequential, divColor="white",
    paste("ICC:", toShow[[ii]][3]), 
    "ICC", lim=c(0, lim_ICC)
  )
  print(q)
  
} 
dev.off()
```

### FC reliability on the brain surface

```{r}
xii0 <- convert_xifti(move_from_mwall(select_xifti(NetMat, 1)))
xii1 <- read_xifti(ciftiTools.files()$cifti["dscalar_ones"], brainstructures="sub")
for (ii in seq(length(toShow))) {
  q <- load_a_result(toShow[[ii]][1], "reliability")
  q <- q$ICC31[[1]][,toShow[[ii]][2]]
  q <- rowMeans(cor_mat(q), na.rm=TRUE)
  q0 <- newdata_xifti(xii0, c(0, q)[1+as.matrix(move_from_mwall(NetMat, 2))[,1]])
  plot(
    q0, title=toShow[[ii]][3], zlim=c(.2, .6), colors = viridis::inferno(255),
    fname=plt_fmt(paste0("FC_reliability_onSurf_", toShow[[ii]][3], ".png"))
  )
  q1 <- newdata_xifti(xii1, c(0, q)[400+as.numeric(xii1$meta$subcort$labels)-2])
  plot(
    q1, title=toShow[[ii]][3], zlim=c(.2, .6), colors = viridis::inferno(255),
    fname=plt_fmt(paste0("FC_reliability_onSub_", toShow[[ii]][3], ".png"))
  )
}
```

### Denoising bar plot comparison

```{r}
bnames <- c("HCP__ICA-FIX", "None", "CompCor", "CSF-WM", "9P", "36P", "CC2MP")
q <- lapply(paste0("Baselines_", bnames), load_a_result)
q <- do.call(cbind, do.call(cbind, lapply(q, function(x){x$ICC31})))
colnames(q)[grepl("HCP__ICA-FIX", colnames(q))] <- "HCP__ICA-FIX"
q <- q[,!grepl("grayo", colnames(q))]
q2 <- t(q[,"CC2MP__06P_DCT4",drop=FALSE]) %*% FC_mask$network$inter[,!(colnames(FC_mask$network$inter)=="all")]
q <- data.frame(
  v = colMeans(q),
  bname = colnames(q)
)

q2 <- data.frame(
  v = c(q2),
  netname = colnames(FC_mask$network$inter)[!(colnames(FC_mask$network$inter)=="all")]
)
q2$netname <- factor(q2$netname, levels=names(color_network))

q$bname_main <- factor(gsub("_DCT0|_DCT4", "", q$bname))
q$DCT <- grepl("DCT4", q$bname)
q$bname_nice <- factor(
  q$bname_main, 
  levels=c(
    "HCP__ICA-FIX",
    "None_", 
    "CompCor__PC01_withCblm", 
    "CompCor__PC02_withCblm", 
    "CompCor__PC05_withCblm", 
    "CompCor__PC10_withCblm", 
    "CSF-WM_", 
    "9P__whole",
    "36P__whole",
    "CC2MP__06P",
    "CC2MP__24P"
  ),
  labels=c(
    "ICA-FIX",
    "MPP", 
    "CC1", 
    "CC2", 
    "CC5", 
    "CC10", 
    "2P", 
    "9P",
    "36P",
    "CC2+MP6",
    "CC2+MP24"
  )
)
q$Detrending <- ifelse(q$DCT, "DCT4", "None")
q$Detrending <- factor(ifelse(q$bname_nice=="ICA-FIX", "HPF", q$Detrending), levels=c("HPF", "DCT4", "None"))

q$show <- q$Detrending != "None" | q$bname_nice=="MPP"
q <- subset(q, show)

q$bname2 <- factor(
  paste0(q$bname_nice, "_", q$Detrending),
  levels = c(
    "ICA-FIX_HPF", "MPP_None", "MPP_DCT4",
    "CC1_DCT4", "CC2_DCT4", "CC5_DCT4", "CC10_DCT4",
    "CC2+MP6_DCT4", "CC2+MP24_DCT4",
    "2P_DCT4", "9P_DCT4", "36P_DCT4"
  )
)

pdf(plt_fmt("FC_reliability_baseline_comparison.pdf"), width=6)

p1 <- ggplot(q, aes(x=bname2, y=v)) +
    geom_bar(stat="identity", 
             #position=position_dodge2(padding=0, preserve="single"), 
             width=.75) +
    geom_vline(xintercept=c(1.5, 3.5, 7.5, 9.5, 11.5), color="black") +
    theme_cowplot() + theme(legend.position="bottom", panel.background = element_rect(fill = NA, color = "black")) +
    xlab("Baseline Denoising") + ylab("Mean ICC") + 
    scale_alpha_manual(values=c(.33, .67, 1)) +
    scale_y_continuous(limits=c(0, .5), expand=expansion(mult=c(0, .01))) +
    scale_x_discrete(expand=expansion(add=.5)) +
    scale_fill_manual(values=as.character(color_m[c("ICAFIX", "darkGray", "lightGray")]))

# p2 <- ggplot(q2, aes(x=netname, y=v, fill=netname)) +
#     geom_bar(
#       stat="identity", color="black",
#       position=position_dodge2(padding=0, preserve="single"), width=.7) +
#     theme_cowplot() + theme(legend.position="bottom", panel.background = element_rect(fill = NA, color = "black")) +
#     xlab("Network") + ylab("Mean ICC") + 
#     scale_alpha_manual(values=c(.33, .67, 1)) +
#     scale_y_continuous(limits=c(0, .5), expand=expansion(mult=c(0, .01))) +
#     scale_x_discrete(expand=expansion(add=.5)) +
#     scale_fill_manual(values=color_network)

p1
#cowplot::plot_grid(plotlist=list(p1, p2), nrow=1, rel_widths=c(.7, .3))

dev.off()

rm(list=setdiff(ls(), varKeep))
```

# 6. Variance components
5. Variance components (MSB, MSR, ICC) with a few denoising methods (ICA-FIX, CC1-10, 36P, CC2+6MP, CC2+24MP -- all with DCT except FIX)

```{r}
plt_idx <- 6

bnames <- c("HCP__ICA-FIX", "None", "CompCor", "CSF-WM", "9P", "36P", "CC2MP")
q <- lapply(paste0("Baselines_", bnames), load_a_result)
q <- list(
  MSB = do.call(cbind, lapply(q, function(x){x$MSB[[1]]})),
  MSR = do.call(cbind, lapply(q, function(x){x$MSR[[1]]})),
  ICC31 = do.call(cbind, lapply(q, function(x){x$ICC31[[1]]}))
)
q <- lapply(q, function(x){
  colnames(x)[grepl("HCP__ICA-FIX", colnames(x))] <- "HCP__ICA-FIX"
  x <- x[,!grepl("grayo", colnames(x))]
  x
})
q <- data.frame(
  v = do.call(c, lapply(q, colMeans)),
  bname = colnames(q[[1]]),
  what = rep(names(q), each=ncol(q[[1]]))
)

q$bname_main <- factor(gsub("_DCT0|_DCT4", "", q$bname))
q$DCT <- grepl("DCT4", q$bname)
q$bname_nice <- factor(
  q$bname_main, 
  levels=c(
    "HCP__ICA-FIX",
    "None_", 
    "CompCor__PC01_withCblm", 
    "CompCor__PC02_withCblm", 
    "CompCor__PC05_withCblm", 
    "CompCor__PC10_withCblm", 
    "CSF-WM_", 
    "9P__whole",
    "36P__whole",
    "CC2MP__06P",
    "CC2MP__24P"
  ),
  labels=c(
    "ICA-FIX",
    "MPP", 
    "CC1", 
    "CC2", 
    "CC5", 
    "CC10", 
    "2P", 
    "9P",
    "36P",
    "CC2\n+ MP6",
    "CC2\n+ MP24"
  )
)
q$Detrending <- ifelse(q$DCT, "DCT4", "None")
q$Detrending <- factor(ifelse(q$bname_nice=="ICA-FIX", "HPF", q$Detrending), levels=c("HPF", "DCT4", "None"))

q <- subset(q, q$Detrending != "None")
q <- subset(q, q$bname_nice %in% levels(q$bname_nice)[c(1,3,4,5,6,9,10,11)])

q$what <- factor(q$what, levels=c("MSB" ,"MSR", "ICC31"))

pdf(plt_fmt("FC_reliability_variance_components.pdf"), width=12.5, height=4)

ggplot(q, aes(x=bname_nice, y=v, fill=Detrending)) +
    geom_bar(stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.6) +
    geom_vline(xintercept=c(1.5, 5.5), color="black") +
    theme_cowplot() + 
    theme(legend.position="bottom", panel.background = element_rect(fill = NA, color = "black")) +
    xlab("Baseline Denoising") + ylab("Value") + 
    scale_y_continuous(limits=c(0, NA), expand=expansion(mult=c(0, .1))) +
    scale_x_discrete(expand=expansion(add=.5)) +
    scale_fill_manual(values=as.character(color_m[c("ICAFIX", "darkGray")])) + 
    facet_wrap(~what, nrow=1, scales="free_y")

dev.off()

rm(list=setdiff(ls(), varKeep))
```

# 7. Scrubbing cutoffs
6. Cutoffs for FD and leverage: add MAP as panel D, add modified FD.  Consider adding trendlines to scatterplots (not a high priority). (edited) 

```{r}
plt_idx <- 7
```

### Projection scrubbing

```{r}
mnames <- c("Lev___ICA", "Lev___fusedPCA", "Lev___PCA")

q <- lapply(paste0("CC2MP6_", mnames), load_a_result)
q <- do.call(cbind, lapply(q, function(x){x$ICC31[[1]]}))
q <- data.frame(
  v = colMeans(q),
  mname = colnames(q)
)
q$cut <- as.numeric(gsub(".*_", "", q$mname))
q$name <- factor(
  gsub("_.*", "", gsub("Lev___", "", q$mname)),
  c("ICA", "fusedPCA", "PCA")
)

q2 <- lapply(paste0("CC2MP6_", mnames), load_a_result, "nScrub")
q2 <- data.frame(
  v = do.call(c, lapply(q2, function(x){colMeans(x$nScrub[[1]], dims=2)})),
  v_25 = do.call(c, lapply(q2, function(x){apply(x$nScrub[[1]], 3, quantile, .25)})),
  v_75 = do.call(c, lapply(q2, function(x){apply(x$nScrub[[1]], 3, quantile, .75)})),
  mname = do.call(c, lapply(q2, function(x){dimnames(x$nScrub[[1]])[[3]]}))
)
q2$cut <- as.numeric(gsub(".*_", "", q2$mname))
q2$name <- factor(
  gsub("_.*", "", gsub("Lev___", "", q2$mname)),
  c("ICA", "fusedPCA", "PCA")
)

baseICC <- mean(load_a_result("CC2MP6_Base")$ICC31[[1]])
dvICC <- mean(load_a_result("CC2MP6_DVARSdual")$ICC31[[1]])
dvnScrub <- mean(load_a_result("CC2MP6_DVARSdual", "nScrub")$nScrub[[1]])

q$v <- q$v - baseICC
q2$v <- q2$v - baseICC
dvICC <- dvICC - baseICC

q <- subset(q, grepl("kurt", q$mname))
rownames(q) <- NULL
q2 <- subset(q2, grepl("kurt", q2$mname))
rownames(q2) <- NULL
```

```{r}
p1 <- ggplot(q, aes(x=cut, y=v, color=name)) + 
  #geom_vline(xintercept=3, color="black", size=1) +
  geom_vline(xintercept=5, size=.8, color=color_m["lightGray"]) +
  geom_hline(yintercept=dvICC, color=as.character(color_m["DVARS"])) +
  geom_hline(yintercept=0, linetype="dashed", color="black") +
  geom_line(size=.8) +
  geom_point(data=q, size=2.2) +
  scale_color_manual(values=as.character(color_m[c("ICA", "FusedPCA", "PCA")])) +
  cowplot::theme_cowplot() +
  scale_y_continuous(breaks=c(-.005, 0, .005)) +
  scale_x_continuous(breaks=c(2,4,6,8,10)) +
  coord_cartesian(xlim=c(1.2, 8.1), ylim=c(-.005, .005)) +
  xlab("Median leverage cutoff") +
  ylab("ICC improvement") + #Mean
  guides(color=guide_legend(nrow=1, title="Projection")) +
  theme(legend.position="bottom")

logjust <- 100
p2 <- ggplot(q2, aes(x=cut, y= logjust + v, color=name)) + 
  geom_vline(xintercept=5, size=.8, color=color_m["lightGray"]) +
  geom_hline(
    yintercept=logjust + dvnScrub, 
    color=as.character(color_m["DVARS"])
  ) +
  # geom_ribbon(aes(ymin=logjust+nScrub.25, ymax=logjust+nScrub.75, fill=name), size=.4, alpha=.5) +
  geom_hline(yintercept=logjust, linetype="dashed", color="black") +
  geom_line(size=.8) +
  geom_point(data=q2, size=2.2) +
  scale_color_manual(values=as.character(color_m[c("ICA", "FusedPCA", "PCA")])) +
  scale_fill_manual(values=as.character(color_m[c("ICA", "FusedPCA", "PCA")])) +
  cowplot::theme_cowplot() +
  scale_y_continuous(
    breaks=logjust + 1185 * c(0, .01, .05, .1, .5), 
    labels=paste0(" ", c(0, 1, 5, 10, 50), "%"),
    trans="log"
  ) +
  scale_x_continuous(breaks=c(2,4,6,8,10)) +
  coord_cartesian(xlim=c(1.2, 8.1), ylim=logjust + 1185 * c(0, .5)) +
  xlab("Median leverage cutoff") +
  ylab("% frames removed") + #Mean
  guides(color=guide_legend(nrow=1, title="Projection")) +
  theme(legend.position="none")

pleg <- cowplot::get_legend(p1)
p1 <- p1 + theme(legend.position="none")

pdf(plt_fmt(paste0("Cutoff_projection.pdf")), height=6, width=3.5)
cowplot::plot_grid(p1, p2, ncol=1, align="hv", axis="tblr")
plot_grid(NULL, pleg, ncol=1)
dev.off()
```

### Motion scrubbing

```{r}
mnames <- c("FD___og___", "FD___og_nfc_l4___")

q <- lapply(paste0("CC2MP6_", mnames), load_a_result)
q <- do.call(cbind, lapply(q, function(x){x$ICC31[[1]]}))
q <- data.frame(
  v = colMeans(q),
  mname = colnames(q)
)
q$cut <- as.numeric(gsub(".*_", "", q$mname))
q$name <- factor(
  gsub("_.*", "", gsub("FD___og_", "", q$mname)),
  c("", "nfc"),
  c("FD", "modFD")
)

q2 <- lapply(paste0("CC2MP6_", mnames), load_a_result, "nScrub")
q2 <- data.frame(
  v = do.call(c, lapply(q2, function(x){colMeans(x$nScrub[[1]], dims=2)})),
  v_25 = do.call(c, lapply(q2, function(x){apply(x$nScrub[[1]], 3, quantile, .25)})),
  v_75 = do.call(c, lapply(q2, function(x){apply(x$nScrub[[1]], 3, quantile, .75)})),
  mname = do.call(c, lapply(q2, function(x){dimnames(x$nScrub[[1]])[[3]]}))
)
q2$cut <- as.numeric(gsub(".*_", "", q2$mname))
q2$name <- factor(
  gsub("_.*", "", gsub("FD___og_", "", q2$mname)),
  c("", "nfc"),
  c("FD", "modFD")
)

baseICC <- mean(load_a_result("CC2MP6_Base")$ICC31[[1]])
dvICC <- mean(load_a_result("CC2MP6_DVARSdual")$ICC31[[1]])
dvnScrub <- mean(load_a_result("CC2MP6_DVARSdual", "nScrub")$nScrub[[1]])

q$v <- q$v - baseICC
q2$v <- q2$v - baseICC
dvICC <- dvICC - baseICC

rownames(q) <- NULL
rownames(q2) <- NULL
```

```{r}
p1 <- ggplot(q, aes(x=cut, y=v, color=name)) + 
  #geom_vline(xintercept=3, color="black", size=1) +
  geom_vline(xintercept=.5, size=.8, color=color_m["lightGray"]) +
  geom_hline(yintercept=dvICC, color=as.character(color_m["DVARS"])) +
  geom_hline(yintercept=0, linetype="dashed", color="black") +
  geom_line(size=.8) +
  geom_point(data=q, size=2.2) +
  scale_color_manual(values=as.character(color_m[c("FD", "modFD")])) +
  cowplot::theme_cowplot() +
  scale_y_continuous(breaks=c(-.005, 0, .005)) +
  scale_x_continuous(breaks=c(2,4,6,8,10)/10) +
  coord_cartesian(xlim=c(1.2, 8.1)/10, ylim=c(-.005, .005)) +
  xlab("Cutoff") +
  ylab("ICC improvement") + #Mean
  guides(color=guide_legend(nrow=1, title="")) +
  theme(legend.position="bottom")

logjust <- 100
p2 <- ggplot(q2, aes(x=cut, y= logjust + v, color=name)) + 
  geom_vline(xintercept=.5, size=.8, color=color_m["lightGray"]) +
  geom_hline(
    yintercept=logjust + dvnScrub, 
    color=as.character(color_m["DVARS"])
  ) +
  # geom_ribbon(aes(ymin=logjust+nScrub.25, ymax=logjust+nScrub.75, fill=name), size=.4, alpha=.5) +
  geom_hline(yintercept=logjust, linetype="dashed", color="black") +
  geom_line(size=.8) +
  geom_point(data=q2, size=2.2) +
  scale_color_manual(values=as.character(color_m[c("FD", "modFD")])) +
  scale_fill_manual(values=as.character(color_m[c("FD", "modFD")])) +
  cowplot::theme_cowplot() +
  scale_y_continuous(
    breaks=logjust + 1185 * c(0, .01, .05, .1, .5), 
    labels=paste0(" ", c(0, 1, 5, 10, 50), "%"),
    trans="log"
  ) +
  scale_x_continuous(breaks=c(2,4,6,8,10)/10) +
  coord_cartesian(xlim=c(1.2, 8.1)/10, ylim=logjust + 1185 * c(0, .5)) +
  xlab("Cutoff") +
  ylab("% frames removed") + #Mean
  guides(color=guide_legend(nrow=1, title="")) +
  theme(legend.position="none")

pleg <- cowplot::get_legend(p1)
p1 <- p1 + theme(legend.position="none")

pdf(plt_fmt(paste0("Cutoff_FD.pdf")), height=6, width=3.5)
cowplot::plot_grid(p1, p2, ncol=1, align="hv", axis="tblr")
plot_grid(NULL, pleg, ncol=1)
dev.off()

rm(list=setdiff(ls(), varKeep))
```

### Num scrubbed vs ICC & MAC

```{r}
mnames <- c(
  "FD___og___", "FD___og_nfc_l4___",
  "Lev___ICA", "Lev___fusedPCA", "Lev___PCA",
  "DVARSdual"
)

q <- lapply(paste0("CC2MP6_", mnames), load_a_result)
q <- do.call(cbind, lapply(q, function(x){x$ICC31[[1]]}))
q2 <- lapply(paste0("CC2MP6_", mnames), load_a_result, "nScrub")
q3 <- lapply(paste0("CC2MP6_", mnames), load_a_result, "mac")
# MAC results were based on script that skipped non-kurt results
q3[seq(3,5)] <- lapply(q3[seq(3,5)], function(x){
  x$mac[[1]] <- c(setNames(rep(NA, 8), "missing"), x$mac[[1]])
  x
})
q <- data.frame(
  v = colMeans(q),
  v2 = do.call(c, lapply(q2, function(x){colMeans(x$nScrub[[1]], dims=2)})),
  v3 = do.call(c, lapply(q3, function(x){x$mac[[1]]})),
  mname = colnames(q)
)
q$cut <- as.numeric(gsub(".*_", "", q$mname))
q <- subset(q, !grepl("PCA__|ICA__|fusedPCA__", q$mname))
q$method <- factor(
  gsub("___.*", "", gsub("Lev___|FD___", "", q$mname)),
  c("og", "og_nfc_l4", "ICA_kurt", "fusedPCA_kurt", "PCA_kurt", "CC2MP6_DVARSdual_1185"),
  c("FD", "modFD", "ICA", "FusedPCA", "PCA", "DVARS")
)

baseICC <- mean(load_a_result("CC2MP6_Base")$ICC31[[1]])
q$v <- q$v - baseICC

q <- subset(q, v2 < hcp_T*.06)
q <- tidyr::pivot_longer(q, c("v", "v3"))
q$name <- factor(q$name, levels=c("v", "v3"), labels=c("ICC(3,1)", "MAC"))
logjust <- 100

q$big <- FALSE
q$big[q$method=="FD" & q$cut==.5] <- TRUE
q$big[q$method=="modFD" & q$cut==.5] <- TRUE
q$big[q$method=="ICA" & q$cut==5] <- TRUE
q$big[q$method=="FusedPCA" & q$cut==5] <- TRUE
q$big[q$method=="PCA" & q$cut==5] <- TRUE
q$big[q$method=="DVARS"] <- TRUE

pdf(plt_fmt(paste0("NumScrubbed_vs_ICC_MAC.pdf")), width=5, height=7)

p1 <- ggplot(q, aes(x=v2 + logjust, y=value, color=method)) + 
  scale_size_manual(values=c(1, 2.8)) +
  geom_vline(
    xintercept=logjust+c(13.886905, 27.877976), alpha=.5, size=1.5,
    color=color_m[["lightGray"]]) +
  geom_hline(yintercept=0, linetype="dashed") +
  #coord_cartesian(ylim=c(-.002, .004)) +
  #geom_point(size=2) + 
  xlab("% frames removed") + ylab("Mean ICC") +
  scale_color_manual(values=color_m[levels(q$method)]) +
  scale_fill_manual(values=color_m[levels(q$method)]) +
  scale_x_continuous(
    breaks=logjust + 1185 * c(0, .01, .02, .05), 
    labels=paste0(" ", c(0, 1, 2, 5), "%"),
    trans="log"
  ) + theme_bw() + 
  labs(color="Scrubbing method") +
  cowplot::theme_cowplot() +
  theme(legend.position = "bottom") +
  facet_grid(name~., scales="free_y")

p1 + geom_line(stat="smooth", method = "lm", formula = y ~ x + I(x^2), alpha=.3, se=FALSE) +
  geom_smooth(method = "lm", formula = y ~ x + I(x^2), aes(fill=method), size=.8, alpha=.1) +
  geom_point(aes(size=big))
p1 + geom_line(size=1, alpha=.5) + geom_point(aes(size=big))

dev.off()
rm(list=setdiff(ls(), varKeep))
```


# 8. Scrubbing overlap
7. Overlap between scrubbing methods (simply update, add modified FD?)

```{r}
plt_idx <- 8

overlap <- readRDS(file.path(dir_analysis, "overlap", "CC2MP6.rds"))
q <- overlap[,,c(5,6),1,drop=FALSE]
overlap[,,c(5,6),1] <- overlap[,,c(5,6),2]
overlap[,,c(5,6),2] <- q
dimnames(overlap)[[3]][c(5,6)] <- c("DVARS__FD", "DVARS__modFD")

pdf(plt_fmt(paste0("Scrubbing_Flag_Overlap_Similarity.pdf")), height=3.5, width=5.5)

overlap2 <- apply(overlap, seq(2,4), sum)
dimnames(overlap2)[[2]] <- gsub("Lev", "", dimnames(overlap2)[[2]])
o_gg <- expand.grid(subject=subjects, pair=dimnames(overlap2)[[2]], what=dimnames(overlap2)[[3]])
o_gg$subject <- factor(o_gg$subject, levels=subjects)
o_gg$what <- factor(o_gg$what, levels=rev(c("first", "both", "second")))
o_gg$value <- c(overlap2)

for (pp in seq(dim(overlap2)[2])) {
  pair0 <- dimnames(overlap2)[[2]][pp]
  pair <- strsplit(pair0, "_")[[1]][c(1,3)]
  pair_cols <- as.character(setNames(color_m, gsub("lev", "", names(color_m)))[pair])
  print(pair)
  o_ggp <- subset(o_gg, pair==pair0)
  order_p <- order(overlap2[,pair0,"first"] + overlap2[,pair0,"both"], decreasing=TRUE)
  o_ggp$subject <- factor(o_ggp$subject, levels=subjects[order_p])
  ymax <- 3000 #if (max(o_ggp$value) > 2000) { 3000 } else { 1800 }
  print(levels(o_ggp$what))
  plt <- ggplot(data=o_ggp, aes(x=subject, y=value, fill=what)) + 
    geom_bar(stat="identity", width=.8) +
    scale_y_continuous(limits=c(0, ymax), expand=c(0,.1)) +
    scale_fill_manual(
      values=rev(c(pair_cols[1], "#00FF00", pair_cols[2])), 
      labels=rev(c(pair[1], "Both", pair[2]))
    ) +
    theme_cowplot() +
    xlab("Subjects") + ylab("Volumes Censored (out of 9600)") + 
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position="bottom")
  print(plt)
}

dev.off()

#rm(list=setdiff(ls(), varKeep))
```

```{r}
plt_idx <- 8

overlap <- readRDS(file.path(dir_analysis, "overlap", "CC2MP62.rds"))

pdf(plt_fmt(paste0("Scrubbing_Flag_Overlap2_Similarity.pdf")), height=3.5, width=5.5)

overlap2 <- apply(overlap, seq(2,4), sum)
dimnames(overlap2)[[2]] <- gsub("Lev", "", dimnames(overlap2)[[2]])
o_gg <- expand.grid(subject=subjects, pair=dimnames(overlap2)[[2]], what=dimnames(overlap2)[[3]])
o_gg$subject <- factor(o_gg$subject, levels=subjects)
o_gg$what <- factor(o_gg$what, levels=c("first", "both", "second"))
o_gg$value <- c(overlap2)

for (pp in seq(dim(overlap2)[2])) {
  pair0 <- dimnames(overlap2)[[2]][pp]
  pair <- strsplit(pair0, "_")[[1]][c(1,3)]
  pair_cols <- as.character(setNames(color_m, gsub("lev", "", names(color_m)))[pair])
  print(pair)
  o_ggp <- subset(o_gg, pair==pair0)
  order_p <- order(overlap2[,pair0,"second"] + overlap2[,pair0,"both"], decreasing=TRUE)
  o_ggp$subject <- factor(o_ggp$subject, levels=subjects[order_p])
  ymax <- 3000 #if (max(o_ggp$value) > 2000) { 3000 } else { 1800 }
  print(levels(o_ggp$what))
  plt <- ggplot(data=o_ggp, aes(x=subject, y=value, fill=what)) + 
    geom_bar(stat="identity", width=.8) +
    scale_y_continuous(limits=c(0, ymax), expand=c(0,.1)) +
    scale_fill_manual(
      values=c(pair_cols[1], "#00FF00", pair_cols[2]), 
      labels=c(pair[1], "Both", pair[2])
    ) +
    theme_cowplot() +
    xlab("Subjects") + ylab("Volumes Censored (out of 9600)") + 
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position="bottom")
  print(plt)
}

dev.off()

#rm(list=setdiff(ls(), varKeep))
```

# 9. Scrubbing effect
8. Effect of scrubbing (update A & B, drop panel C)

### Bar plots

```{r}
plt_idx <- 9

mnames <- c(
  "Base",
  "FD___og___", "FD___og_nfc_l4___",
  "Lev___ICA", "Lev___fusedPCA", "Lev___PCA",
  "DVARSdual"
)
mnames2 <- c(
  "FD___og___0.5", "FD___og_nfc_l4___0.5", 
  "Lev___ICA_kurt___5", "Lev___fusedPCA_kurt___5", "Lev___PCA_kurt___5",
  "CC2MP6_DVARSdual_1185"
)
mnames3 <- c("FD", "modFD", "ICA", "FusedPCA", "PCA", "DVARS")

q <- lapply(paste0("CC2MP6_", mnames), load_a_result)
q <- do.call(cbind, lapply(q, function(x){x$ICC31[[1]]}))
q <- q[,seq(2, 66)] - q[,1] # take diff from base
FC_mask2 <- cbind(
  CC = FC_mask$bs$intra[,"left"]>0 | FC_mask$bs$intra[,"right"]>0,
  CS = (FC_mask$bs$inter[,"left"]>0 | FC_mask$bs$inter[,"right"]>0) & (
    FC_mask$bs$inter[,"subcort"]>0
  ),
  SS = FC_mask$bs$intra[,"subcort"]>0
)
FC_mask2 <- apply(FC_mask2, 2, function(x){x/sum(x)})
q <- cbind(
  t(q) %*% FC_mask$network$inter,
  t(q) %*% FC_mask2,
  t(q) %*% FC_mask$group$inter[,seq(47, 51)]
)

q <- q[mnames2,]

q <- data.frame(
  mname = rownames(q),
  v = as.numeric(q),
  group = rep(colnames(q), each=nrow(q))
)
q$group <- factor(q$group, levels=Net$levels, labels=Net$labels)
q$mname <- factor(q$mname, levels=c(mnames2))
```

```{r}
p1 <- ggplot(subset(q, group %in% levels(group)[seq(10)]), aes(x=group, y=v)) + 
  geom_bar(aes(fill=mname), stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.75) +
  geom_hline(yintercept=0, linetype="dashed") +
  scale_fill_manual(values=as.character(color_m[mnames3])) +
  scale_y_continuous(limits=c(-.01, .03), expand=c(0, 0)) +
  cowplot::theme_cowplot() + theme(legend.position="none")

p1a <- p1 + geom_col(
    fill=rep(c(color_network, color_m[["altPink"]]), each=6), 
    data=function(x){for (ii in seq(ncol(x))){x[[ii]] <- as.numeric(x[[ii]])}; x*0+.01/60}
  )

p2 <- ggplot(subset(q, group %in% levels(group)[seq(11,15)]), aes(x=group, y=v)) + 
  geom_bar(aes(fill=mname), stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.75) +
  geom_hline(yintercept=0, linetype="dashed") +
  scale_fill_manual(values=as.character(color_m[mnames3])) +
  scale_y_continuous(limits=c(-.01, .03), expand=c(0, 0)) +
  cowplot::theme_cowplot() + theme(legend.position="none")

p3 <- ggplot(subset(q, group %in% levels(group)[seq(16,18)]), aes(x=group, y=v)) + 
  geom_bar(aes(fill=mname), stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.75) +
  geom_hline(yintercept=0, linetype="dashed") +
  scale_fill_manual(values=as.character(color_m[mnames3])) +
  scale_y_continuous(limits=c(-.01, .03), expand=c(0, 0)) +
  cowplot::theme_cowplot() + theme(legend.position="none")

pdf(plt_fmt(paste0("Scrubbing_Effect_Reliability_Breakdown.pdf")), height=5, width=11)
cowplot::plot_grid(p1, p2, p3, ncol=3, rel_widths=c(10+2, 5+2, 3+2))
p1a
dev.off()
```

```{r}
p1 <- ggplot(subset(q, (!grepl("PCA", q$mname)) & group %in% levels(group)[seq(10)]), aes(x=group, y=v)) + 
  geom_bar(aes(fill=mname), stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.75) +
  geom_hline(yintercept=0, linetype="dashed") +
  scale_fill_manual(values=as.character(color_m[mnames3[!grepl("PCA", mnames3)]])) +
  scale_y_continuous(limits=c(-.01, .03), expand=c(0, 0)) +
  cowplot::theme_cowplot() + theme(legend.position="none")

p1a <- p1 #+ geom_col(
    #fill=rep(c(color_network, color_m[["altPink"]]), each=6), 
    #data=function(x){for (ii in seq(ncol(x))){x[[ii]] <- as.numeric(x[[ii]])}; x*0+.01/60}
#  )

p2 <- ggplot(subset(q, (!grepl("PCA", q$mname)) & group %in% levels(group)[seq(11,15)]), aes(x=group, y=v)) + 
  geom_bar(aes(fill=mname), stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.75) +
  geom_hline(yintercept=0, linetype="dashed") +
  scale_fill_manual(values=as.character(color_m[mnames3[!grepl("PCA", mnames3)]])) +
  scale_y_continuous(limits=c(-.01, .03), expand=c(0, 0)) +
  cowplot::theme_cowplot() + theme(legend.position="none")

p3 <- ggplot(subset(q, (!grepl("PCA", q$mname)) & group %in% levels(group)[seq(16,18)]), aes(x=group, y=v)) + 
  geom_bar(aes(fill=mname), stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.75) +
  geom_hline(yintercept=0, linetype="dashed") +
  scale_fill_manual(values=as.character(color_m[mnames3[!grepl("PCA", mnames3)]])) +
  scale_y_continuous(limits=c(-.01, .03), expand=c(0, 0)) +
  cowplot::theme_cowplot() + theme(legend.position="none")

pdf(plt_fmt(paste0("Scrubbing_Effect_Reliability_Breakdown_less.pdf")), height=5, width=11)
cowplot::plot_grid(p1, p2, p3, ncol=3, rel_widths=c(10+2, 5+2, 3+2))
p1a
dev.off()
```

### Grid plot

```{r}
qB <- load_a_result("CC2MP6_Base")$ICC31[[1]][,1]

pdf(plt_fmt("FC_reliability_grid_scrubbing.pdf"))
for (ii in seq(length(mnames2))) {
  q <- load_a_result(paste0("CC2MP6_", mnames[[ii+1]]))
  q <- q$ICC31[[1]][,mnames2[[ii]]] - qB
  q <- ggcorrplot2(
    q, coloring$diverging4, divColor="white",
    paste("Change in ICC:", mnames3[[ii]]), 
    "Change in ICC", lim=lim_cICC
  )
  print(q)
} 

dev.off()

pdf(plt_fmt("FC_reliability_grid_scrubbing2.pdf"))
for (ii in seq(length(mnames2))) {
  q <- load_a_result(paste0("CC2MP6_", mnames[[ii+1]]))
  q <- q$ICC31[[1]][,mnames2[[ii]]] - qB
  q <- ggcorrplot2(
    q, coloring$diverging4, divColor="white",
    paste("Change in ICC:", mnames3[[ii]]), 
    "Change in ICC", lim=lim_cICC/2
  )
  print(q)
} 

dev.off()

rm(list=setdiff(ls(), varKeep))
```

# 10. PCC & SMOT FC

### Baseline grid plot

```{r}
plt_idx <- 10

qB <- load_a_result("CC2MP6_Base", "meanFC")$meanFC[[1]][,1]
qB <- cor_mat(qB)

idx_PCC <- c(4, 202)
idx_SMA <- c(157, 355)
idx <- c(idx_PCC, idx_SMA)
idx_names <- c("PCC-L", "PCC-R", "SMOT-L", "SMOT-R")

qB <- qB[rev(idx),idx]

pdf(plt_fmt(paste0("FC_PCC_SMOT_Baseline_Grid.pdf")), height=4, width=4)


ggcorrplot(qB, outline.color = color_m[["darkGray"]], title="Baseline FC", digits=12) + 
  scale_y_continuous(breaks=c(1, 2, 3, 4), labels=rev(idx_names)) +
  scale_x_continuous(breaks=c(1, 2, 3, 4), labels=idx_names) +
  coord_equal(expand=FALSE) +
  coloring$diverging7(
    c(-lim_FC, lim_FC), guide=guide_colorbar(title="FC", ticks.colour = "black", ticks.linewidth = 1), 
    labels = function(x){gsub("0.", ".", x, fixed=TRUE)}, na.value="red"
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.text.y = element_text(margin=margin(r=10)),
    axis.text.x = element_text(margin=margin(r=10)),
    #axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "bottom"#, legend.text.align = 1
  )

dev.off()
```

### Line width values

```{r}
mnames <- c(
  "Base",
  "FD___og___", "FD___og_nfc_l4___",
  "Lev___ICA", "Lev___fusedPCA", "Lev___PCA",
  "DVARSdual"
)
mnames2 <- c(
  "FD___og___0.5", "FD___og_nfc_l4___0.5", 
  "Lev___ICA_kurt___5", "Lev___fusedPCA_kurt___5", "Lev___PCA_kurt___5",
  "CC2MP6_DVARSdual_1185"
)
mnames3 <- c("FD", "modFD", "ICA", "FusedPCA", "PCA", "DVARS")

q <- lapply(paste0("CC2MP6_", mnames), load_a_result, "meanFC")
q <- do.call(cbind, lapply(q, function(x){x$meanFC[[1]]}))
q <- q[,seq(2, 66)] - q[,1] # take diff from base
q <- q[,mnames2]

for (ii in seq(length(mnames2))) {
  z <- cor_mat(q[,ii])
  z <- z[idx,idx]
  z <- z[lower.tri(z)]
  print(c(mnames3[[ii]], 
    mean(z[c(1,6)]) - mean(z[seq(2,5)])
  ))
}
```

```{r}
z <- expand.grid(
  p1 = seq(4),
  p2 = seq(4)
)
z$idx <- NA

for (ii in seq(nrow(z))) {
  if (z$p1[ii] == z$p2[ii]) { next }
  q <- matrix(FALSE, nrow=parc_res2, ncol=parc_res2)
  q[idx[z$p1[ii]], idx[z$p2[ii]]] <- TRUE
  q[idx[z$p2[ii]], idx[z$p1[ii]]] <- TRUE
  q <- q[upper.tri(q)]
  z$idx[ii] <- which(q)
}

z$p1n <- c("PCC-L", "PCC-R", "SMOT-L", "SMOT-R")[z$p1]
z$p2n <- c("PCC-L", "PCC-R", "SMOT-L", "SMOT-R")[z$p2]
```

### Parcels on surface

```{r}
NetMat2 <- transform_xifti(
  NetMat,
  function(x){ifelse(x %in% c(idx_PCC, idx_SMA), x, 0)}
)
plot(
  NetMat2, view="medial",
  fname=plt_fmt(paste0("FC_PCC_SomMotA_Legend.png"))
)
```

### Bar plot

```{r}
mnames <- c(
  "Base",
  "FD___og___", "FD___og_nfc_l4___",
  "Lev___ICA", "Lev___fusedPCA", "Lev___PCA",
  "DVARSdual"
)
mnames2 <- c(
  "FD___og___0.5", "FD___og_nfc_l4___0.5", 
  "Lev___ICA_kurt___5", "Lev___fusedPCA_kurt___5", "Lev___PCA_kurt___5",
  "CC2MP6_DVARSdual_1185"
)
mnames3 <- c("FD", "modFD", "ICA", "FusedPCA", "PCA", "DVARS")

q <- lapply(paste0("CC2MP6_", mnames), load_a_result, "meanFC")
q <- do.call(cbind, lapply(q, function(x){x$meanFC[[1]]}))
q <- q[,seq(2, 66)] - q[,1] # take diff from base
q <- q[,mnames2]
net_mask <- FC_mask$network$inter[,"Default"] & FC_mask$network$inter[,"SomMot"]
q <- data.frame(
  method = mnames3,
  v1 = colMeans(q[!FC_mask$bs$inter[,"subcort"],]), # Mean change within the cortex
  v2 = colMeans(q[net_mask,]), # Mean change among DMN-SomMot connections
  c1 = q[z$idx[1],],  # This change
  c2 = q[z$idx[2],],  # This change
  c3 = q[z$idx[3],],  # This change
  c4 = q[z$idx[4],]  # This change
)

q <- tidyr::pivot_longer(q, cols=seq(2,7))
q$name <- factor(q$name, 
  levels=c("v1", "v2", "c1", "c2", "c3", "c4"),
  labels = c(
    c("All inter-cortex"),
    c("All DMN-SomMot"),
    c("PCC-L & SMA-L"),
    c("PCC-R & SMA-L"),
    c("PCC-L & SMA-R"),
    c("PCC-R & SMA-R")
  )
)
q$method <- factor(q$method, levels=mnames3)

pdf(plt_fmt(paste0("FC_PCC_SomMotA.pdf")), height=5, width=9)

ggplot(q, aes(x=method, y=value, fill=name)) + 
  geom_bar(stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.75) +
  geom_hline(yintercept=0, linetype="dashed") +
  scale_fill_manual(
    values=c(
      color_m[["darkGray"]], color_m[["lightGray"]], 
      "darkblue", "purple4", "slateblue", "royalblue1"),
    name="Connection(s)") +
  theme_cowplot() + ylab("Change in FC strength") + xlab("Scrubbing method")

dev.off()

rm(list=setdiff(ls(), varKeep))
```

# 11. Fingerprinting
11. Fingerprinting

```{r}
plt_idx <- 11

score_fingerprint <- function(fp){
  q <- expand.grid(dimnames(fp))
  q <- cbind(q, c(fp))
  q <- subset(q, grepl("_on", q$Var1))
  q2 <- aggregate(q[,"c(fp)"], by=list(q$Var1), mean)
  colnames(q2) <- c("network", "fp_score")
  q2
}

mnames <- c(
  "Base",
  "FD___og___", "FD___og_nfc_l4___",
  "Lev___ICA", "Lev___fusedPCA", "Lev___PCA",
  "DVARSdual"
)
mnames2 <- c(
  "CC2MP6_Base_1185",
  "FD___og___0.5", "FD___og_nfc_l4___0.5", 
  "Lev___ICA_kurt___5", "Lev___fusedPCA_kurt___5", "Lev___PCA_kurt___5",
  "CC2MP6_DVARSdual_1185"
)
mnames3 <- c("Baseline", "FD", "modFD", "ICA", "FusedPCA", "PCA", "DVARS")

q <- load_a_result(c(paste0("CC2MP6_", mnames)), "fingerprinting")
# Fix missing method names
q2 <- load_a_result(c(paste0("CC2MP6_", mnames)), "MAC")$MAC
for (ii in seq(length(q2))) {
  names(q$fingerprinting[[ii]]) <- names(q2[[ii]])
}
q <- do.call(c, q$fingerprinting)
q <- lapply(q, score_fingerprint)
q <- q[mnames2]
q <- data.frame(
  v = do.call(c, lapply(q, function(x){x$fp_score})),
  net = gsub("_on", "", q[[1]]$network),
  method = rep(names(q), each=nrow(q[[1]]))
)

q$method <- factor(q$method, levels=c(mnames2), labels=c(mnames3))
q$net <- factor(q$net, levels=c("All", Net$levels), labels=c("All", Net$labels))
```

```{r}
pdf(plt_fmt(paste0("Fingerprinting.pdf")), height=5, width=3.5)

ggplot(subset(q, !grepl("PCA", method) & method=="Baseline"), aes(y=v, x=reorder(net, -v), fill=net)) +
  geom_bar(stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.85) +
  scale_fill_manual(
    values=c(color_m[["altPink"]], as.character(color_network[Net$levels][seq(2,10)])),
    name="Network",
    labels=setNames(Net$levels, Net$labels)
  ) +
  
  theme_cowplot() +
  scale_y_continuous(limits=c(0, 1), expand=c(0, 0)) +
  theme(legend.position="bottom", axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  ylab("Fingerprinting match rate") + xlab("")

dev.off()
```

```{r}
q <- load_a_result(c(paste0("CC2MP6_", mnames)), "fingerprinting")
# Fix missing method names
q2 <- load_a_result(c(paste0("CC2MP6_", mnames)), "MAC")$MAC
for (ii in seq(length(q2))) {
  names(q$fingerprinting[[ii]]) <- names(q2[[ii]])
}
q <- do.call(c, q$fingerprinting)
q <- lapply(q, score_fingerprint)
q <- q[mnames2]
for (ii in seq(2, length(q))) {
  q[[ii]]$fp_score <- q[[ii]]$fp_score - q[[1]]$fp_score
}
q <- data.frame(
  v0 = q[[1]]$fp_score,
  v = do.call(c, lapply(q, function(x){x$fp_score})),
  net = gsub("_on", "", q[[1]]$network),
  method = rep(names(q), each=nrow(q[[1]]))
)

q$method <- factor(q$method, levels=c(mnames2), labels=c(mnames3))
q$net <- factor(q$net, levels=c("All", Net$levels), labels=c("All", Net$labels))
```

```{r}
pdf(plt_fmt(paste0("Fingerprinting_change.pdf")), height=5, width=5.5)

ggplot(subset(q, method!="Baseline"), aes(y=v, x=reorder(net, -v0), fill=method)) +
  geom_bar(stat="identity", position=position_dodge2(padding=0, preserve="single"), width=.65) +
  scale_fill_manual(
    values=color_m[mnames3[mnames3!="Baseline"]],
    name="Method",
    labels=setNames(Net$levels, Net$labels)
  ) +
  
  theme_cowplot() +
  scale_y_continuous(limits=c(-.02, .05), expand=c(0, 0), breaks=c(-.02, 0, .05)) +
  theme(legend.position="bottom") +
  ylab("Match rate improvement") + xlab("")

dev.off()

rm(list=setdiff(ls(), varKeep))
```

# 12. Prediction
12. Prediction accuracy (drop coefficient matrices)

```{r}
plt_idx <- 12

dev <- function(p, p2=NULL){ if(is.null(p2)){p2<-p}; 2 * ( p2*log(1/p) + (1-p2)*log(1/(1-p)) ) }
Gender_dev <- c(true = dev(mean(hcp_dg_S1200$Gender=="M")))
score_preds <- function(preds, what="Sex") {
  switch(what,
    Sex = mean(dev(preds, rep(as.numeric(hcp_dg_S1200$Gender) - 1, each=4)))
  )
}
devTrue <- dev(mean(hcp_dg_S1200$Gender=="M"))

mnames <- c(
  "Base",
  "FD___og___", "FD___og_nfc_l4___",
  "Lev___ICA",
  "DVARSdual"
)
mnames2 <- c(
  "CC2MP6_Base_1185",
  "FD___og___0.5", "FD___og_nfc_l4___0.5", 
  "Lev___ICA_kurt___5", 
  "CC2MP6_DVARSdual_1185"
)
mnames3 <- c("Baseline", "FD", "modFD", "ICA", "DVARS")

rvars <- c("Sex")#, "Cog_F", "Cog_M")

q <- q2 <- setNames(vector("list", length(mnames)), mnames3)
for (ii in seq(length(mnames))) {
  q[[ii]] <- q2[[ii]] <- setNames(vector("list", length(rvars)), rvars)
  for (rvar in rvars) {
    z <- file.path(
      dir_analysis, "pred", rvar,
      paste0(c(seq(5), seq(11, 20)), 
             "_CC2MP6_", mnames[ii], "_1185_S1200.rds")
    )
    # z <- list.files(
    #   file.path(dir_analysis, "pred", rvar), paste0("CC2MP6_", mnames[ii]),
    #   full.names=TRUE
    # )
    z <- lapply(z, readRDS) 
    q[[ii]][[rvar]] <- lapply(z, function(x){x[[1]]$preds})
    q2[[ii]][[rvar]] <- lapply(z, function(x){x[[1]]$alpha_best})
  }
}

qS <- setNames(vector("list", length(mnames)), mnames3)
for (ii in seq(length(mnames))) {
  z <- lapply(q[[ii]]$Sex, function(x){
    dev(x, rep(as.numeric(hcp_dg_S1200$Gender)-1, each=4))
  })
  z <- do.call(cbind, z)
  qS[[ii]] <- colMeans(z)
}

qS <- do.call(cbind, qS)

qg <- data.frame(
  method = colnames(qS),
  mu = colMeans(qS),
  sigma = apply(qS, 2, sd)/sqrt(15)
)

qg$method <- factor(qg$method, levels=c("Baseline", "FD", "modFD", "ICA", "DVARS"))

pdf(plt_fmt(paste0("Prediction_Sex.pdf")), height=4.5, width=7)

p1 <- ggplot(qg, aes(x=method, y=mu, color=method)) + 
  scale_x_discrete(expand=c(.05,.05)) +
  geom_errorbar(aes(ymin=mu-sigma, ymax=mu+sigma), width=.3) + geom_point(size=3, stat="identity") +
  scale_color_manual(values=color_m[mnames3]) +
  scale_y_continuous(limits=c(.6, .7)) +
  theme_cowplot() + ylab("Mean CV prediction error (sex)") + xlab("Method") +
  theme(legend.position="none", panel.spacing = unit(2, "lines")) 

p2 <- ggplot(qg, aes(x=method, y=mu, color=method)) + 
  scale_x_discrete(expand=c(.05,.05)) +
  geom_hline(yintercept=c(.6, .7)) +
  geom_errorbar(aes(ymin=mu-sigma, ymax=mu+sigma), width=.3) + geom_point(size=3, stat="identity") +
  geom_hline(yintercept=devTrue, linetype="dashed") +
  scale_color_manual(values=color_m[mnames3]) +
  theme_cowplot() + ylab("Mean CV prediction error (sex)") + xlab("Method") +
  theme(legend.position="none", panel.spacing = unit(2, "lines")) 

cowplot::plot_grid(p1, p2, nrow=1)

dev.off()
```

Total cognition

```{r}
# mseTrue <- var(rep(hcp_dg_S1200$CogTotalComp_Unadj, each=4), na.rm=TRUE)
# 
# qCF <- setNames(vector("list", length(mnames)), mnames3)
# for (ii in seq(length(mnames))) {
#   z <- lapply(q[[ii]]$Cog_F, function(x){
#     mean((x - rep(hcp_dg_S1200$CogTotalComp_Unadj, each=4))^2, na.rm=TRUE)
#   })
#   z <- do.call(cbind, z)
#   qCF[[ii]] <- colMeans(z)
# }
# qCF <- do.call(cbind, qCF)
# 
# mseTrue <- var(rep(hcp_dg_S1200$CogTotalComp_Unadj, each=4), na.rm=TRUE)
# 
# qCM <- setNames(vector("list", length(mnames)), mnames3)
# for (ii in seq(length(mnames))) {
#   z <- lapply(q[[ii]]$Cog_M, function(x){
#     mean((x - rep(hcp_dg_S1200$CogTotalComp_Unadj, each=4))^2, na.rm=TRUE)
#   })
#   z <- do.call(cbind, z)
#   qCM[[ii]] <- colMeans(z)
# }
# qCM <- do.call(cbind, qCM)
```

# 999. ICC improvements with different baselines

```{r}
plt_idx <- 999

mnames <- c(
  "Base",
  "FD___og___", "FD___og_nfc_l4",
  "Lev___ICA", "Lev___fusedPCA", "Lev___PCA",
  "DVARSdual"
)
mnames2 <- c(
  "FD___og___0.5", "FD___og_nfc_l4___0.5", 
  "Lev___ICA_kurt___5", "Lev___fusedPCA_kurt___5", "Lev___PCA_kurt___5",
  "CC2MP6_DVARSdual_1185"
)
mnames3 <- c("FD", "modFD", "ICA", "FusedPCA", "PCA", "DVARS")

bnames <- c("DCT4", "CC5", "9P", "36P", "CC2MP6")

q0 <- setNames(vector("list", length(bnames)), bnames)
for (bname in bnames) {
  cat(bname, "\n")
  mnamesb <- c(
    paste0(bname, "_Base_1185"),
    mnames2[seq(5)],
    paste0(bname, "_DVARSdual_1185")
  )
  if (bname=="CC2MP6") { mnames[3] <- "FD___og_nfc_l4___"  }
  q <- lapply(paste0(bname, "_", mnames), load_a_result)
  q <- do.call(cbind, lapply(q, function(x){x$ICC31[[1]]}))
  #q <- q[,seq(2, 66)] - q[,1] # take diff from base
  q0[[bname]] <- q[,mnamesb]
}

qg <- lapply(q0, colMeans)
qg <- data.frame(
  base = rep(names(q0), each=ncol(q0[[1]])),
  value = do.call(c, qg),
  method = c("Base", mnames3)
)
qg$group <- paste0("g", seq(nrow(qg)))
qg2 <- data.frame(
  base = rep(names(q0), each=ncol(q0[[1]])),
  value = do.call(c, lapply(q0, function(x){rep(colMeans(x)[1], ncol(x))})),
  method = c("Base", mnames3),
  group = paste0("g", seq(nrow(qg)))
)
qg <- rbind(qg, qg2)
qg$base <- factor(qg$base, levels=bnames)
qg$method <- factor(qg$method, levels=c("Base", mnames3))
qg$group <- factor(qg$group, levels=paste0("g", seq(nrow(qg2))))

qg2$base <- factor(qg2$base, levels=bnames)
qg2$method <- factor(qg2$method, levels=c("Base", mnames3))
qg2$group <- factor(qg2$group, levels=paste0("g", seq(nrow(qg2))))

pdf(plt_fmt(paste0("AltBaselines_ICC.pdf")), height=6.5, width=5)

ggplot() +
  geom_line(aes(x=base, y=value, color=method, group=group), data=subset(qg, method!="Base"), size=3, position=position_dodge(width=.9)) +
  geom_errorbar(aes(x=base, ymin=value, ymax=value), data=qg2, size=1.2) +
  scale_y_continuous(limits=c(.3, .5), expand=c(0,0)) +
  #geom_point(aes(x=name, y=value, color=method), data=subset(thing, method!="Base"), size=2, position=position_dodge(width=.2)) +
  xlab("") + ylab("Mean ICC") +
  scale_color_manual(values=color_m[mnames3]) +
  theme_cowplot() + 
  theme(legend.position="bottom")

dev.off()
```

```{r}
q0 <- setNames(vector("list", length(bnames)), bnames)
for (bname in bnames) {
  cat(bname, "\n")
  mnamesb <- c(
    paste0(bname, "_Base_400"),
    mnames2[seq(5)],
    paste0(bname, "_DVARSdual_400")
  )
  #if (bname=="CC2MP6") { mnames[3] <- "FD___og_nfc_l4___"  }
  q <- lapply(paste0(bname, "_", mnames), load_a_result, nT=400)
  q <- do.call(cbind, lapply(q, function(x){x$ICC31[[1]]}))
  #q <- q[,seq(2, 66)] - q[,1] # take diff from base
  q0[[bname]] <- q[,mnamesb]
}

qg <- lapply(q0, colMeans)
qg <- data.frame(
  base = rep(names(q0), each=ncol(q0[[1]])),
  value = do.call(c, qg),
  method = c("Base", mnames3)
)
qg$group <- paste0("g", seq(nrow(qg)))
qg2 <- data.frame(
  base = rep(names(q0), each=ncol(q0[[1]])),
  value = do.call(c, lapply(q0, function(x){rep(colMeans(x)[1], ncol(x))})),
  method = c("Base", mnames3),
  group = paste0("g", seq(nrow(qg)))
)
qg <- rbind(qg, qg2)
qg$base <- factor(qg$base, levels=bnames)
qg$method <- factor(qg$method, levels=c("Base", mnames3))
qg$group <- factor(qg$group, levels=paste0("g", seq(nrow(qg2))))

qg2$base <- factor(qg2$base, levels=bnames)
qg2$method <- factor(qg2$method, levels=c("Base", mnames3))
qg2$group <- factor(qg2$group, levels=paste0("g", seq(nrow(qg2))))

#pdf(plt_fmt(paste0("AltBaselines_ICC_nT400.pdf")), height=6.5, width=5)

ggplot() +
  geom_line(aes(x=base, y=value, color=method, group=group), data=subset(qg, method!="Base"), size=3, position=position_dodge(width=.9)) +
  geom_errorbar(aes(x=base, ymin=value, ymax=value), data=qg2, size=1.2) +
  #scale_y_continuous(limits=c(.3, .5), expand=c(0,0)) +
  #geom_point(aes(x=name, y=value, color=method), data=subset(thing, method!="Base"), size=2, position=position_dodge(width=.2)) +
  xlab("") + ylab("Mean ICC") +
  scale_color_manual(values=color_m[mnames3]) +
  theme_cowplot() + 
  theme(legend.position="bottom")

#dev.off()

rm(list=setdiff(ls(), varKeep))
```

# 999. In-depth scrubbing cutoff comparison

```{r}
plt_idx <- 999

pfun <- function(ggx, xlim=NULL, xbreaks=NULL, ylim=NULL){
  ggplot(ggx, aes(x=cut, y=value, color=network)) + 
      #geom_vline(xintercept=.5, linetype="solid", color="black", alpha=.1, size=4) +
      #geom_vline(xintercept=5, linetype="solid", color="black", alpha=.1, size=4) +
      geom_hline(yintercept=0, linetype="dashed", color="black") +
      geom_line(aes(group=network), alpha=.7, size=1) +
      geom_point(data=subset(ggx, network=="all"), size=2.2) + 
      facet_grid(what~subgroup) +
      scale_fill_manual(values=ggcols) +
      scale_color_manual(values=ggcols) + 
      cowplot::theme_cowplot() + 
      scale_y_continuous(limits=c(-Inf, Inf)) +
      scale_x_continuous(breaks=xbreaks, limits=c(-Inf, Inf)) +
      theme(panel.background = element_rect(fill = NA, color = "black"),
            legend.position="none") +
      ggtitle(paste0("Change from baseline, T=", nT[tt])) +
      coord_cartesian(xlim=xlim, ylim=ylim)
}

snames <- c(
  "Base",
  "FD___og___", "FD___og_nfb___", "FD___og_nfc___", 
  #"FD___dt___", "FD___dt_nfb___", "FD___dt_nfc___", 
  "FD___og_l4___", "FD___og_nfb_l4___", "FD___og_nfc_l4___",
  #"FD___dt_l4___", "FD___dt_nfb_l4___", "FD___dt_nfc_l4___",
  "DVARSdual"
)
nT <- c(400, 800, 1185)

# Load MSB, MSR, and ICC31 for all baseline methods, for all nT 
sICC <- setNames(vector("list", length(nT)), paste0("T", nT))
for (tt in seq(length(sICC))) {
  sICC[[tt]] <- lapply(
    file.path(dir_analysis, "reliability", paste0("CC2MP6_", snames, "_", nT[tt], ".rds")),
    readRDS
  )
  sICC[[tt]] <- list(
    MSB=do.call(cbind, lapply(sICC[[tt]], `[[`, "MSB")),
    MSR=do.call(cbind, lapply(sICC[[tt]], `[[`, "MSR")),
    ICC31=do.call(cbind, lapply(sICC[[tt]], `[[`, "ICC31"))
  )
  sICC[[tt]] <- lapply(sICC[[tt]], function(x){x[,!grepl("0.1", colnames(x))]})
  # Summarize by network.
  sICC[[tt]] <- lapply(
    sICC[[tt]], 
    function(x){ t(FC_mask$network$inter) %*% x }
  )
}

# Load n scrub similarly

# Take differences from baseline
sICCd <- lapply(sICC, function(x){lapply(x, function(y){y-y[,1]})})
sICCpd <- lapply(sICC, function(x){lapply(x, function(y){(y-y[,1])/y[,1]*100})})

ggs_ICC <- get_ggs(sICC, "FD")
gg_sICCd <- subset(get_ggs(sICCd, "FD"), method != "Base")
gg_sICCpd <- subset(get_ggs(sICCpd, "FD"), method != "Base")

ggcols <- Labs[!duplicated(Labs$network),c("network", "network_color")]
ggcols$network <- as.character(ggcols$network)
ggcols <- rbind(ggcols, c("all", "#000000"))
ggcols <- setNames(ggcols$network_color, ggcols$network)

pdf(plt_fmt(paste0("Motion_cutoff_ICC_expanded.pdf")), height=11, width=12)

for (tt in seq(length(nT))) {
  
  ggs_this <- gg_sICCd[!gg_sICCd$dt & gg_sICCd$nT==paste0("T", nT[tt]),]
  
  # ggdv <- sICCd[[paste0("T", nT[tt])]][["ICC31"]][,paste0("CC2MP6_DVARSdual_", nT[tt])]
  # ggdv <- data.frame(
  #   network=names(ggdv), 
  #   method=NA, what=NA, 
  #   nT=paste0("T", nT[tt]), 
  #   value=as.numeric(ggdv), 
  #   dt=NA, l4=NA, filter2=NA, filter=NA, subgroup="DVARS", cut=.5
  # )
  
  levels(ggs_this$subgroup) <- c(levels(ggs_this$subgroup), "DVARS")
  ggs_this$subgroup[ggs_this$method=="DVARSdual"] <- "DVARS"
  ggs_this$cut[ggs_this$method=="DVARSdual"] <- .4
  ggs_this_dvext <- subset(ggs_this, ggs_this$method=="DVARSdual")
  ggs_this_dvext$cut <- .6
  ggs_this <- rbind(ggs_this, ggs_this_dvext)
  
  # ggplot(ggs_this, aes(x=cut, y=value, color=network)) + 
  #   geom_vline(xintercept=.5, linetype="solid", color="black", alpha=.1, size=4) +
  #   geom_hline(yintercept=0, linetype="dashed", color="black") +
  #   geom_line(aes(group=network), alpha=.7, size=1) +
  #   geom_point(data=subset(ggs_this, network=="all"), size=2.2) + 
  #   facet_grid(what~subgroup, scale="free_y") +
  #   scale_fill_manual(values=ggcols) +
  #   scale_color_manual(values=ggcols) + 
  #   cowplot::theme_cowplot() + 
  #   scale_x_continuous(breaks=c(.2, .4, .6, .8)) +
  #   scale_y_continuous(expand=expansion(mult=ifelse(tt==1, 0, .1)*c(-1, 1))) +
  #   theme(panel.background = element_rect(fill = NA, color = "black")) +
  #   ggtitle(paste0("Change from baseline, T=", nT[tt])) +
  #   coord_cartesian(xlim=c(.28, .8))
  
  p1 <- pfun(
    subset(ggs_this, ggs_this$what=="MSB"), 
    xlim=c(.2, .8), xbreaks=c(.2, .4, .6, .8), 
    ylim=c(-.01, .01)
  )
  p2 <- pfun(
    subset(ggs_this, ggs_this$what=="MSR"), 
    xlim=c(.2, .8), xbreaks=c(.2, .4, .6, .8), 
    ylim=c(-.001, .0005)
  )
  p3 <- pfun(
    subset(ggs_this, ggs_this$what=="ICC31"), 
    xlim=c(.2, .8), xbreaks=c(.2, .4, .6, .8), 
    ylim=c(-.01, .015)
  )
  print(cowplot::plot_grid(p1, p2, p3, ncol=1, align="hv", rel_heights=c(1,1,1.7)))
}
dev.off()

plt_idx <- 999

snames <- c("Base", "Lev___PCA", "Lev___fusedPCA", "Lev___ICA", "DVARSdual")

# Load MSB, MSR, and ICC31 for all baseline methods, for all nT 
sICC <- setNames(vector("list", length(nT)), paste0("T", nT))
for (tt in seq(length(sICC))) {
  sICC[[tt]] <- lapply(
    file.path(dir_analysis, "reliability", paste0("CC2MP6_", snames, "_", nT[tt], ".rds")),
    readRDS
  )
  sICC[[tt]] <- list(
    MSB=do.call(cbind, lapply(sICC[[tt]], `[[`, "MSB")),
    MSR=do.call(cbind, lapply(sICC[[tt]], `[[`, "MSR")),
    ICC31=do.call(cbind, lapply(sICC[[tt]], `[[`, "ICC31"))
  )
  sICC[[tt]] <- lapply(sICC[[tt]], function(x){x[,!grepl("0.1", colnames(x))]})
  # Summarize by network.
  sICC[[tt]] <- lapply(
    sICC[[tt]], 
    function(x){ t(FC_mask$network$inter) %*% x }
  )
}

# Load n scrub similarly

# Take differences from baseline
sICCd <- lapply(sICC, function(x){lapply(x, function(y){y-y[,1]})})
sICCpd <- lapply(sICC, function(x){lapply(x, function(y){(y-y[,1])/y[,1]*100})})

ggs_ICC <- get_ggs(sICC, "Proj")
gg_sICCd <- subset(get_ggs(sICCd, "Proj"), method != "Base")
gg_sICCpd <- subset(get_ggs(sICCpd, "Proj"), method != "Base")

ggcols <- Labs[!duplicated(Labs$network),c("network", "network_color")]
ggcols$network <- as.character(ggcols$network)
ggcols <- rbind(ggcols, c("all", "#000000"))
ggcols <- setNames(ggcols$network_color, ggcols$network)

#gg_sICCd <- subset(gg_sICCd, method2 != "DVARSdual")
gg_sICCd$subgroup <- factor(paste0(
  gg_sICCd$method2, ifelse(gg_sICCd$kurt, "", "_noKurt")),
  levels=c("ICA", "fusedPCA", "PCA", "ICA_noKurt", "fusedPCA_noKurt", "PCA_noKurt", "DVARSdual")
)

pdf(plt_fmt(paste0("Projection_cutoff_ICC_expanded.pdf")), height=11, width=12)

for (tt in seq(length(nT))) {
  
  ggs_this <- gg_sICCd[gg_sICCd$nT==paste0("T", nT[tt]),]
  
  levels(ggs_this$subgroup) <- c(levels(ggs_this$subgroup), "DVARS")
  ggs_this$subgroup[ggs_this$method=="DVARSdual"] <- "DVARS"
  ggs_this$cut[ggs_this$method=="DVARSdual"] <- 4
  ggs_this_dvext <- subset(ggs_this, ggs_this$method=="DVARSdual")
  ggs_this_dvext$cut <- 6
  ggs_this <- rbind(ggs_this, ggs_this_dvext)
  # ggplot(ggs_this, aes(x=cut, y=value, color=network)) + 
  #   geom_vline(xintercept=.5, linetype="solid", color="black", alpha=.1, size=4) +
  #   geom_hline(yintercept=0, linetype="dashed", color="black") +
  #   geom_line(aes(group=network), alpha=.7, size=1) +
  #   geom_point(data=subset(ggs_this, network=="all"), size=2.2) + 
  #   facet_grid(what~subgroup, scale="free_y") +
  #   scale_fill_manual(values=ggcols) +
  #   scale_color_manual(values=ggcols) + 
  #   cowplot::theme_cowplot() + 
  #   scale_x_continuous(breaks=c(.2, .4, .6, .8)) +
  #   scale_y_continuous(expand=expansion(mult=ifelse(tt==1, 0, .1)*c(-1, 1))) +
  #   theme(panel.background = element_rect(fill = NA, color = "black")) +
  #   ggtitle(paste0("Change from baseline, T=", nT[tt])) +
  #   coord_cartesian(xlim=c(.28, .8))
  
  p1 <- pfun(
    subset(ggs_this, ggs_this$what=="MSB"), 
    xlim=c(2, 8), xbreaks=c(2, 4, 6, 8), 
    ylim=c(-.01, .005)
  )
  p2 <- pfun(
    subset(ggs_this, ggs_this$what=="MSR"), 
    xlim=c(2, 8), xbreaks=c(2, 4, 6, 8), 
    ylim=c(-.001, .0005)
  )
  p3 <- pfun(
    subset(ggs_this, ggs_this$what=="ICC31"),
    xlim=c(2, 8), xbreaks=c(2, 4, 6, 8), 
    ylim=c(-.01, .015)
  )
  print(cowplot::plot_grid(p1, p2, p3, ncol=1, align="hv", rel_heights=c(1,1,1.7)))
}
dev.off()
```

# 999. Prediction coefficient

```{r}
plt_idx <- 999

q <- readRDS(file.path(dir_analysis, "pBetas/Sex", "CC2MP6_Base_1185_S1200.rds"))
q <- q$CC2MP6_Base_1185_S1200$betas
pdf(plt_fmt("FC_pBetas.pdf"))
q <- ggcorrplot2(
  q, coloring$diverging2, divColor="black",
  paste("Sex prediction model coefficients: CC2+MP6"), 
  "Beta", lim=.015
)

print(q)
dev.off()

xii0 <- convert_xifti(move_from_mwall(select_xifti(NetMat, 1)))
xii1 <- read_xifti(ciftiTools.files()$cifti["dscalar_ones"], brainstructures="sub")
q <- readRDS(file.path(dir_analysis, "pBetas/Sex", "CC2MP6_Base_1185_S1200.rds"))
q <- q$CC2MP6_Base_1185_S1200$betas
q <- rowMeans(cor_mat(q), na.rm=TRUE)
q0 <- newdata_xifti(xii0, c(0, q)[1+as.matrix(move_from_mwall(NetMat, 2))[,1]])
plot(
  q0, title="CC2MP6 Betas", zlim=c(-.005, .005), colors = rev(RColorBrewer::brewer.pal(name="PuOr", n=9)),
  fname=plt_fmt(paste0("FC_pBetas_onSurf_Base.png"))
)
q1 <- newdata_xifti(xii1, c(0, q)[400+as.numeric(xii1$meta$subcort$labels)-2])
plot(
  q1, title="CC2MP6 Betas", zlim=c(-.005, .005), colors = rev(RColorBrewer::brewer.pal(name="PuOr", n=9)),
  fname=plt_fmt(paste0("FC_pBetas_onSub_Base.png"))
)
```